Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-06-07 paper-v1.tex
Citations from important reports done yesterday night

\begin{document}
%
\title{Ants-Review: A Protocol For Open Anonymous Peer-Reviews}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Bianca Trovò\inst{1,2}\orcidID{0000-0002-6776-2304}\thanks{Correspondent author} \and
Nazzareno Massari\inst{3,4}\orcidID{0000-0002-6638-2174}}
%
\authorrunning{B. Trovò et N. Massari}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Sorbonne Université, Faculté des Sciences et Ingénierie, 75005 Paris, France \and
Neurospin research center, CEA/SAC/DSV/I2BM, 91191 Gif-sur-Yvette, France
\email{bianca.trovo@alumni.unitn.it}\\
\and
Alma Mater Politecnico di Torino, 10129 Turin, Italy\and
Independent Blockchain Engineer, London, UK \\
\email{nazzareno@nazzarenomassari.com}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Peer-review is a necessary and essential quality control step for scientific publications. However, the process, which is very costly in terms of time investment, not only is not remunerated but it’s also not recognized by the academic community as a relevant scientific output for a researcher. Therefore, scientific dissemination is affected. Here, to solve this issue we propose a blockchain-based incentive protocol that rewards scientists also for their contributions to other scientists’ work and that builds up a reputational system. We designed a basic Bounty-like contract called AntsReview that allows any author to issue a call for peer-reviewing their scientific publication. If requirements are met, peer-reviews will be audited by an external editor and payed by the Issuer. To promote ethical behaviour the system will implement a quadratic funding on AntsReview.
\keywords{Blockchain  \and Peer-review \and Privacy \and Incentivization.}
\end{abstract}
%
%
\section{Introduction}
blockchain for science here and application to open science and to peer review as a specific case

An increasing body of voices in the scientific community has started to speak up for the need of updating current scientific practices with the advances represented by blockchain technology [2, 8]. As an example, we refer to a ‘manifesto’ written by a few anonymous authors, proposing a blockchain based system of academic endorsement (AES) [1]. Indeed, we could say that in general “specific blockchain characteristics meet the requirements of an open science infrastructure” [3-7]:
\paragraph{Decentralisation}Taking out the need of intermediaries, would make useless depending on highly profiting publishing companies for disseminating scientific work and managing the rules of the peer-review process;
\paragraph{Immutability} of the system in which information can only be appended with tamper proof-time stamping,  but not subsequently modified, would secure the intellectual property and a fairer measure of the scientific contribution of the actors at play during the multiple versions of a paper;
\paragraph{Transparency} (meaning that we have a viewable record of all the papers and peer-reviews), would also make editorial decisions (publish or not publish a study) more transparent and democratic. Finally, cryptographic hashing could allow for a double-blind process that reduces human biases in judgement by assigning hashed pseudonymous to universal researcher identifiers. From all these aspects taken together, a more democratic open peer-review  process could rise, in which merit and power (of access to information, of decision…) is more equally redistributed among the stakeholders (researchers, reviewers, taxpayers).
\newline The paper is structured as follows. Sections 2 presents research background and related works. Section 3 explains the proposed Ethereum-based protocol illustrating the system architecture and the current status of implementation. In Sect. 4 we discuss the implication of our work. Section 5 contains the conclusions. Appendixes present the smart contracts.

\section{Background}
\subsection{Peer-review: a flawed and outdated system}
Peer-review is the traditional and necessary process at the heart of quality control in science [9, 12], determining the destinies of articles’ publications and therefore of scientific dissemination. However, the current peer-review system is outdated: in the past, it was effective when scholarly communication happened exclusively through printed paper journals, but nowadays, with the high and fast-paced levels of articles productions, its slow and multistage process doesn’t keep up with the times.
\subsubsection{It's a slow multi-stage process.} Indeed, articles submitted to journals can take from months to years after editors’ first scrutiny, going back and forth several review rounds before acceptance for publications.
\paragraph{Traditional peer-review process} This section takes inspiriration from the editorial processes at Nature Methods and Wiley.
\begin{enumerate}
    \item The author submits a manuscript to the journal.
    \item  An editorial team  assesses the paper for what concerns the requirements of the journal's Author's Guideline (composition, sections...).
    \item An Editor in Chief (EIC) is assigned to the manuscript and checks if the paper meets the scopes of the journal and novelty criteria. If the paper is rejected, it does not go through the consideration process and the editor notifies the author.
    \item If the editorial decision is to send the manuscript for review, the handling editor looks for potential reviewers. Potential reviewers can be suggested by the authors themselves, but usually it's up to the editor to find researchers in the field who are competent enough but not closely related to the study to review.
    \item Candidate reviewers receive the journal's invitation and evaluate acceptance based on their own level of expertise, intrinsic conﬂicts of interest and time availability. They then accept or decline. If they decline, they might suggest alternative reviewers. Editors keep searching for reviewers until they find two or three reviewers who agree to review the manuscript.
    \item When reviewers engage themselves in delivering peer-review report by a certain deadline, the author(s) are notified. The reviewers identity is usually only know to the editor but is hidden to the authors or the other reviewers themselves.
    \item Reviewers independently conduct their reviews by exposing in their reports strengths and weaknesses of the manuscript in a point-by-point fashion and submitting a final recommendation to the editor: acceptance, rejection or revision (major or minor).
    \item the handling editor or the editorial team considers all the submitted reports and makes the final decision.
    \item If the decision is a major or minor revision, authors are invited to re-submit a corrected or improved version of the manuscript with a letter to the reviewers. The same reviewers might be contacted again and if they want they can follow up the peer-review process.
    \item If the decision is a rejection, the editor might indicate another journal where to submit the manuscript.

@@

\subsection{Related work}
Credit for peer review is not a new thing: mostly journals handled it so far with virtual 'badges', certificates of performance, citation in annual editorials but none of these is standardized in a way that has a weight for funders world ranking bodies institutions like imapct factor h-index.
In relation to security issues \emph{CryptSubmit} \emph{MaRSChain}
\emph{Crossref} primary DOI provider, announced that review reports could be now registered as part of their services
\emph{Publons} provides a way to keep track of the reviews records and integrate them into academic profiles such as ORCID
ScienceOpen
\emph{DEIP}
Rubriq provides independent and standardized peer review that can be accepted and shared across all types of journals and distribution systems. Now absorbed by Research Square.
\emph{Peerage of Science} that provides a journal-independent free service for scientific peer review and publishing. The interesting feature is that it provides also a peer-review of the reviews.
\emph{Blockchain for Peer Review,}pilot project sponsored by Digital Science and Katalysis, aims at developing a protocol for storing peer reviews submitted by publishers on a blockchain such that review process can be independently verified and review info is fed to ORCID researcher profiles []
\emph{ReviewCoin}
\emph{I8X Platform}

@@

\section{System concept}
In this paper we propose Ants-Review, a new incentivisation mechanism built on a distributed platform that issues open peer-reviews to validate scientific papers while preserving the anonymity of its contributors and that . We imagine a final paper originating from the peer-review process as a complex system that emerges from the product of interactions between the authors and the reviewers, a whole that is more than the sum of its parts. Therefore, the name hints at the ant colony as a model of self-organization in which all micro-contributions of the individuals add up to complex behaviour.
A previous version of this paper can be found here \cite{10.5281/zenodo.3828087}, as a proposal submitted for the ETH Turin 2020 Hackathon.
and it’s design and attempt of implementation are exposed in the following section.
Here I expose the main traits/features of AR
\begin{itemize}
\item accountability: both for recognition and for security vs fraud abuse etc we need to be able to track back the identities of the contributors to a peer-review to make sure there are no conflict of interest. this means the platform acts like a version control system where commit are permanent and hashed 
\item transparency of the records: all reviews should be open access to the community to prevent waste of knowledge and disrupt the secretive system of black boxes of peer reviews in journals that centralize all the reports 
\item incentivisation: via symbolic and material recognition of the performed work. tokens and bounty
\item inclusiveness via gamification: all the community is involved in the process - no selection process feeling of belonging -- quadratic voting and share of the stake
\end{itemize}

In the following sessions we describe the architecture of the system and its building blocks

@@

\begin{enumerate}
    \item The author submits a manuscript to the journal.
    \item If the papers passes stage 2-3 of editorial decision (appropriateness of style and coherence with the journal's scope)
    \item the editor issues a bounty (\emph{bounty issuance}) for the paper review. Fulfillment rules are set in a smart-contract.
    \item (footnote?) the bounty prize could correspond to part of the article submission fees and article publication fees requested to the authors by the journal.
    \item Reviews fulfilling the smart-contract requirements are validated by the journal editors.
    \item When the reviews are accepted (\emph{bounty fulfillment}), reviewers awarded a token called \emph{ANT}.
    \item Not all reviews will have the same quality and depth. However, each of them might bring up one or more relevant contribution for the sake of improving the manuscript. In order to redistribute the bounty in a fair manner across reviewers, reviews will be voted by the editors with Quadratic Voting.********* POINT OF FAILURE? who votes?

@@

AntsReview [Fig.\ref{fig:contracts}] is a distributed peer-review system which synthesizes successful ideas from previous systems including The Bounty Network[ref], ERC20[ref], AZTEC Protocol[ref], IPFS[ref], Proof of Existence[ref], ...

@@

AntsReview [\ref{appendix:b}] is the core of the smart contracts deployed on Ethereum Rinkeby's Testnet as shown in the flow-chart[img].
\newline It implements a Bounty-like system where an issuer (author) is asked a series of actions, to ensure transparency and robustness, regarding the AntReview that he's creating:
\begin{itemize}
  \item to upload the file containing the requirements of the peer-review and the paper into IPFS.
  \item to specify a deadline in the form of a unix timestamp after which the fulfillment will no longer be accepted.
  \item to send the amount of ether for the reward.
\end{itemize}

AntsReviewRoles[appendix A], to ensure integrity of the system, implements an access management, leveraging on AccessControl.sol by OpenZeppelin Library, through the creation of the Roles Issuer and Peer-Reviewer[code].
\newline It also integrates a circuit breaker deisgn pattern via Pausable.sol by OpenZeppelin to allow the Pauser Role, that by default is the Owner of the Smart Contracts, to pause (or unpause) the functions in case of emergency.
\newline In this way, only the Issuer (author) can create a new AntReview.
\newline Once created, an AntReview is available to be fulfilled by Peer-Reviewers, uploading the peer-review on IPFS before the deadline.
\newline The AntReview after being validated is then accepted by the Issuer and paid equally between Peer-Reviewers.
\newline Also, the Issuer can cancel the AntReview at any time and withdraw the amount of ether staked.
\newline One of the key aspects of the protocol is the concept of Proof of Existence, introduced by Stuart Haber \& W. Scott Stornetta with the paper "How to time-stamp a digital document".
\newline As the pioneers of blockchain an cited by Bitcoin whitepaper, they were in a mission to solve the problem of immutability of digital records that became reality with the Blockchain and Bitcoin as its first application.
\newline In Ethereum the concept of immutability is achieved via the blockchain and proof of work consesus algorithm by a chain of timestamped block hashes that are secured by miners competing computations.
\newline AntsReview is evaluating the advantages of storing the hashes of the peer-reviews into a Merkle Tree to achieve immutability and efficiency in verifying the data with a complexity of O(logn) for searching through the tree.
\newline A Merkle tree is a particular type of binary tree, formed by a set of nodes with a large set of leaf nodes at the bottom of the tree containing representing the hash of the original data, a set of intermediate nodes where each node is the sum of the two children hashes, ending with a single root hash.
\newline In order to verify if a spefic hash is included into a Markle Tree, leveraging on MerkleProof.sol by OpenZeppelin Library, we need to provide a proof, generated from the leaf of interest, that rapresent the remification derived from the leaf, the root hash and finally the leaf we want to verify.
\newline The paper and peer-review documents will be included into a Merkle Tree by hashing the data using keccak256, a cryptographic hashing algorithm available in Solidiy, an object-oriented programming language for writing smart contracts that run on the Ethereum Virtual Machine (EVM).

@@

\begin{itemize}
  \item PseudoAnonimity granted by an Etherum's Externally Owned Accounts (EOA) address that can pseudo-obscure the identity of the agent.
  \item Private Transactions allowed by AZTEC Protocol security layer via zkAnt. Future developments will allow to leverage on PLONK Proofs to reduce gas costs and improve scalability.
\end{itemize}

>>>>

\begin{document}
%
\title{Ants-Review: A Protocol For Open Anonymous Peer-Reviews}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Bianca Trovò\inst{1,2}\orcidID{0000-0002-6776-2304}\thanks{Correspondent author} \and
Nazzareno Massari\inst{3,4}\orcidID{0000-0002-6638-2174}}
%
\authorrunning{B. Trovò et N. Massari}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Sorbonne Université, Faculté des Sciences et Ingénierie, 75005 Paris, France \and
Neurospin research center, CEA/SAC/DSV/I2BM, 91191 Gif-sur-Yvette, France
\email{bianca.trovo@alumni.unitn.it}\\
\and
Alma Mater Politecnico di Torino, 10129 Turin, Italy\and
Independent Blockchain Engineer, London, UK \\
\email{nazzareno@nazzarenomassari.com}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Peer-review is a necessary and essential quality control step for scientific publications. However, the process, which is very costly in terms of time investment, not only is not remunerated but it’s also not recognized by the academic community as a relevant scientific output for a researcher. Therefore, scientific dissemination is affected. Here, to solve this issue we propose a blockchain-based incentive protocol that rewards scientists also for their contributions to other scientists’ work and that builds up a reputational system. We designed a basic Bounty-like contract called AntsReview that allows any author to issue a call for peer-reviewing their scientific publication. If requirements are met, peer-reviews will be audited by an external editor and payed by the Issuer. To promote ethical behaviour the system will implement a quadratic funding on AntsReview.
\keywords{Blockchain  \and Peer-review \and Privacy \and Incentivization.}
\end{abstract}
%
%
\section{Introduction}
blockchain for science here and application to open science and to peer review as a specific case
to cite "" The essence of blockchain is that it allows transactions of value without intermediaries, and can enable decentralised business models." "

Dr. Soenke Bartling is a German radiologist and founder of Blockchain for Science2, a think tank based in Berlin. Launched in 2016, its aim is to ‘open up science and knowledge creation by means of the blockchain (r)evolution’. Besides meetings, hackathons3 and stimulating knowledge sharing through its online platform, the organisation also launched and maintains a living document4 on blockchain and science, collecting ideas on how blockchain could open up science and knowledge creation.

\begin{itemize}
\item reproducibility crisis (a fix)
\item openness of access and data 
\item 'blockchainefied science':  "a more flexible, grass-root and reputation-based governance of science."
\end{itemize}
reputation metrics -- "blockchain would make much larger parts of the research cycle open to scientific self-correction. This bears the potential to be a new approach to the current reproducibility crisis in science, and could ‘reduce waste and make more research results true’. Beyond that, blockchain could be used to reduce overhead and accelerate the scientific process and incentivise true innovation." https://docs.google.com/document/d/1Uhjb4K69l0bSx7UXYUStV_rjuPC7VGo0ERa-7xEsr58/edit#heading=h.z4w0uvttpvgt
Decentralized
Distributed 
Immutable (≈’append only database’)
Transparent (provable to the external world)
"One such system, the Ethereum blockchain, goes so far as to provide its own programming language to run distributed, unstoppable, and provable applications [27]. This includes smart contracts [28] which can be used to realize distributed, autonomous applications and organizations [29]." they propose permissioned public blockchain for science
"Figure 3: Large parts of the research cycle can make use of blockchain (yellow arch); only the experiment/initial data collection itself cannot. From data collection onwards, the rest of the research circle would then become immutable, comprehensible, and externally provable. This would make larger parts of the research cycle open to scientific self-correction and may make more research results reproducible, true, and useful."
\begin{itemize}
\item scientific ideas/data/lab notebooks via time-stamping and proof of existence - Blockchains provide a ‘notarization’ functionality.
\item pre-registration in open science, now managed by open platforms like OSF 
\item The recommendation to reduce waste in science which reads: ‘Public availability of raw data and complete scripts of statistical analysis could be required by journals and funding agencies sponsoring new research’ [5,49] could be realized through blockchain. 
to prevent vs publication bias (reporting only positive results) or p-hacking or ex-post-facto hypothesizing (changing the hypothesis after having looked into the data)
\item stress on scientific self-correction: from open data science to blockchain based science 
\end{itemize}
"Figure 5: In closed science, scientists just publish a description of their research data and results in their final publication (I). Currently, researchers can publish their research data in data repositories, but that leaves no trace of the data collection or handling process (II). Of course, the final repository could be a blockchain based, decentralized database (III). However, blockchain technology could take the whole process one step further: the whole data handling process could take place in a blockchain system and would therefore be provable and open to scientific self-correction (at will) (IV)." 
Blockchain systems make it possible to publish research anonymously [70] or with a second online identity - and yet one could still get money or other research impact appreciation for it [71,72]
Science reputation systems can be built using blockchain without a trusted third party. 
As such, a Decentralized Autonomous Academic Endorsement System has been proposed and interesting implementation ideas and next implementation steps have been disclosed [72].
Research funding: A DARO (distributed autonomous research organization) allocates and distributes research resources.
could also engage the public through a more transparent research process. 
token economy could be applied to scientific ideas and groundbreaking discoveries, we could incentivise scientist to spread ideas early and strongly. This stands in contrast to the current system, which incentivises scientists to remain inert until publication, patent application, etc. It has been claimed that this could also be a solution to the famous innovators dilemma [9
What should token for science/research projects represent? One thing would be ‘asset-backed’ tokens as described here [96] as a bet on the commercially usable part of the intellectual property. However, is that enough? Couldn't there be tokens that represent a purely scientific value of a research project? Researchers are used to immaterial rewards called “reputation”. For instance, I could place bets (as outlined below on relativity and will receive reputation tokens for properly predicting outcomes. I would also receive “reputation” if my own research results can be validated by “the crowd” or will be used by their future work, i.e. represent the equivalent of citations.)  
The blockchain revolution is a game changer and hence chances are that this can be used to break with inappropriate cultures. Indeed, blockchain technology could be used to ‘Increase value and reduce waste’ [5], by opening the research cycle to scientific self-control beyond the final publication and might therefore be a fix to the current reproducibility crisis in science.

Through the blockchain, ownership of content is automatically established, and the use of content and the payment of royalties are executed through smart contracts in which the rights are stored."

commercial landscape in scholarly communication. For example, the platforms allow micropayments t
New Metrics Research on the blockchain could have a huge impact on the way researchers build their reputation and become recognised.The big advantage of a blockchain for research is that all activities of scientists can be automatically stored.Whenever a researcher uploads data, performs statistical analyses, writes and submits an article or reviews a manuscript, this is automatically tracked and recorded. By working on a blockchain, the risk of fraud is significantly reduced making it significantly easier to collect reliable and complete data on the performance of researchers, research groups and universities.This would allow for more sophisticated as well as reliable metrics to be built on top of that. Moreover, it will allow metrics to be based on activities that are currently not well recognised (e.g., peer review).
Alternative Economic Models
A blockchain for research could accompany the introduction of a cryptocurrency, which would add an economic layer to the blockchain. This ‘bitcoin for research’ could be used to make micro payments to publishers for consuming content, and could also introduce a monetary reward scheme to researchers themselves. For example, the blockchain could disintermediate publishers and reward authors directly with cryptocurrencies that can be used to purchase other content or services. It could also introduce rewards for research activities, such as peer review, statistical support, exchange of lab equipment, outsourcing specific research, or the hosting of data. Eventually, initial coin offerings (ICOs12), a form of crowdfunding using cryptocurrencies, could be used to fund entire research projects. In this way, a crypto economy could evolve in science reflecting the value merits of a number of activities.

REWRITE
An increasing body of voices in the scientific community has started to speak up for the need of updating current scientific practices with the advances represented by blockchain technology [2, 8]. As an example, we refer to a ‘manifesto’ written by a few anonymous authors, proposing a blockchain based system of academic endorsement (AES) [1]. Indeed, we could say that in general “specific blockchain characteristics meet the requirements of an open science infrastructure” [3-7]:
\paragraph{Decentralisation}Taking out the need of intermediaries, would make useless depending on highly profiting publishing companies for disseminating scientific work and managing the rules of the peer-review process;
\paragraph{Immutability} of the system in which information can only be appended with tamper proof-time stamping,  but not subsequently modified, would secure the intellectual property and a fairer measure of the scientific contribution of the actors at play during the multiple versions of a paper;
\paragraph{Transparency} (meaning that we have a viewable record of all the papers and peer-reviews), would also make editorial decisions (publish or not publish a study) more transparent and democratic. Finally, cryptographic hashing could allow for a double-blind process that reduces human biases in judgement by assigning hashed pseudonymous to universal researcher identifiers. From all these aspects taken together, a more democratic open peer-review  process could rise, in which merit and power (of access to information, of decision…) is more equally redistributed among the stakeholders (researchers, reviewers, taxpayers).

\newline The paper is structured as follows. Sections 2 presents research background and related works. Section 3 explains the proposed Ethereum-based protocol illustrating the system architecture and the current status of implementation. In Sect. 4 we discuss the implication of our work. Section 5 contains the conclusions. Appendixes present the smart contracts.

\section{Background}
\subsection{Peer-review: a flawed and outdated system}

"Peer review In recent years a lot of attention has been given to fundamental problems associated with the peer review process which lies at the heart of scholarly communication5,6,7.The perceived problems are multiple.There is a lack of visibility and recognition for reviewers, with their review work remaining largely unnoticed.Together, the increased number of manuscripts submitted to journals, and a subsequent need for more reviewers, leads to an increasing difficulty in finding suitable reviewers.Additionally, there is a perceived bias against women in the review process8.There are also cases of review manipulation, sometimes involving identity fraud which forced publishers to retract articles9. Overall, the review process is considered opaque and expensive, slowing down the speed of scientific discovery and progress."

Peer-review is the traditional and necessary process at the heart of quality control in science [9, 12], determining the destinies of articles’ publications and therefore of scientific dissemination. However, the current peer-review system is outdated: in the past, it was effective when scholarly communication happened exclusively through printed paper journals, but nowadays, with the high and fast-paced levels of articles productions, its slow and multistage process doesn’t keep up with the times.
\subsubsection{It's a slow multi-stage process.} Indeed, articles submitted to journals can take from months to years after editors’ first scrutiny, going back and forth several review rounds before acceptance for publications.
\paragraph{Traditional peer-review process} This section takes inspiration from the editorial processes at \emph{Nature Methods} and \emph{Wiley}.
\begin{enumerate}
    \item The author submits a manuscript to the journal.
    \item  An editorial team  assesses the paper for what concerns the requirements of the journal's Author's Guideline (composition, sections...).
    \item An Editor in Chief (EIC) is assigned to the manuscript and checks if the paper meets the scopes of the journal and novelty criteria. If the paper is rejected, it does not go through the consideration process and the editor notifies the author.
    \item If the editorial decision is to send the manuscript for review, the handling editor looks for potential reviewers. Potential reviewers can be suggested by the authors themselves, but usually it's up to the editor to find researchers in the field who are competent enough but not closely related to the study to review.
    \item Candidate reviewers receive the journal's invitation and evaluate acceptance based on their own level of expertise, intrinsic conﬂicts of interest and time availability. They then accept or decline. If they decline, they might suggest alternative reviewers. Editors keep searching for reviewers until they find two or three reviewers who agree to review the manuscript.
    \item When reviewers engage themselves in delivering peer-review report by a certain deadline, the author(s) are notified. The reviewers identity is usually only know to the editor but is hidden to the authors or the other reviewers themselves.
    \item Reviewers independently conduct their reviews by exposing in their reports strengths and weaknesses of the manuscript in a point-by-point fashion and submitting a final recommendation to the editor: acceptance, rejection or revision (major or minor).
    \item the handling editor or the editorial team considers all the submitted reports and makes the final decision.
    \item If the decision is a major or minor revision, authors are invited to re-submit a corrected or improved version of the manuscript with a letter to the reviewers. The same reviewers might be contacted again and if they want they can follow up the peer-review process.
    \item If the decision is a rejection, the editor might indicate another journal where to submit the manuscript.

@@

\subsection{Related work}
Credit for peer review is not a new thing: mostly journals handled it so far with virtual 'badges', certificates of performance, citation in annual editorials but none of these is standardized in a way that has a weight for funders world ranking bodies institutions like imapct factor h-index.
In relation to security issues \emph{CryptSubmit} \emph{MaRSChain}
\emph{Crossref} primary DOI provider, announced that review reports could be now registered as part of their services
\emph{Publons} provides a way to keep track of the reviews records and integrate them into academic profiles such as ORCID
ScienceOpen
\emph{DEIP}
Rubriq provides independent and standardized peer review that can be accepted and shared across all types of journals and distribution systems. Now absorbed by Research Square.
\emph{Peerage of Science} that provides a journal-independent free service for scientific peer review and publishing. The interesting feature is that it provides also a peer-review of the reviews.
\emph{Blockchain for Peer Review,}pilot project sponsored by Digital Science and Katalysis, aims at developing a protocol for storing peer reviews submitted by publishers on a blockchain such that review process can be independently verified and review info is fed to ORCID researcher profiles []
\emph{ReviewCoin}
\emph{I8X Platform}
A more comprehensive reform of academic endorsement has been proposed in the manifesto ‘Towards Open Science:The Case for a Decentralized Autonomous Endorsement System11’, published anonymously.The author(s) propose a new academic endorsement system that is not based on current journal publication practices which are argued to be expensive, slow, disregard non-traditional output and negative results, and which give too much power to editors and publishers. Built on the blockchain, the Academic Endorsement System (AES) is based on a new form of currency, coined academic endorsement points (AEP), which can be used by scientists to reward scientific work that is worthy of endorsement. Moreover, the amount of AEP credited to a scientist is based on the AEP received for previous work. Researchers whose output has been endorsed to a high degree will have a larger influence in the community. Any kind of research output could be endorsed, for example blog posts, data sets, software etc.Another advantage is that this system would be faster than the time it takes for citation metrics to accrue.
The startup Matryx.ai13 aims to transform the nature of research collaboration itself. Its initiators claim that one of the problems with current scientific practices is its incentive structure. Scientific awards, for example, are based on competition rather than on collaboration, despite the fact that new ideas are usually collaborative in nature. Moreover, different researchers and research groups are often working on the same problems, wasting, as they claim on their website,‘brain power’, time and money. Matryx intends to provide a platform enabling and incentivising research collaboration while discouraging solitary and siloed research. On Matryx, a research project starts when users set a bounty on a problem that they want the community to solve. Contributors solve these problems by working with each other on the platform.The collaboration is tracked through the blockchain thus ensuring contributors are credited appropriately when the problem is solved. In principle, everyone can contribute in the collaboration: scientists, PhD students and even enthusiastic amateurs.

@@

\section{System concept}
In this paper we propose Ants-Review, a new incentivisation mechanism built on a distributed platform that issues open peer-reviews to validate scientific papers while preserving the anonymity of its contributors and that . We imagine a final paper originating from the peer-review process as a complex system that emerges from the product of interactions between the authors and the reviewers, a whole that is more than the sum of its parts. Therefore, the name hints at the ant colony as a model of self-organization in which all micro-contributions of the individuals add up to complex behaviour.
A previous version of this paper can be found here \cite{10.5281/zenodo.3828087}, as a proposal submitted for the ETH Turin 2020 Hackathon.
and it’s design and attempt of implementation are exposed in the following section.
Here I expose the main traits/features of AR
\begin{itemize}
\item accountability: both for recognition and for security vs fraud abuse etc we need to be able to track back the identities of the contributors to a peer-review to make sure there are no conflict of interest. this means the platform acts like a version control system where commit are permanent and hashed 
\item transparency of the records: all reviews should be open access to the community to prevent waste of knowledge and disrupt the secretive system of black boxes of peer reviews in journals that centralize all the reports 
\item incentivisation: via symbolic and material recognition of the performed work. tokens and bounty
\item inclusiveness via gamification: all the community is involved in the process - no selection process feeling of belonging -- quadratic voting and share of the stake
\end{itemize}
crowdfunding schemes leveraged by blockchain technology
In the following sessions we describe the architecture of the system and its building blocks
AntsReview [Fig.\ref{fig:contracts}] is a distributed peer-review system which synthesizes successful ideas from previous systems including The Bounty Network[ref], ERC20[ref], AZTEC Protocol[ref], IPFS[ref], Proof of Existence[ref], ...

@@

\begin{enumerate}
    \item The author submits a manuscript to the journal.
    \item If the papers passes stage 2-3 of editorial decision (appropriateness of style and coherence with the journal's scope)
    \item the editor issues a bounty (\emph{bounty issuance}) for the paper review. Fulfillment rules are set in a smart-contract.
    \item (footnote?) the bounty prize could correspond to part of the article submission fees and article publication fees requested to the authors by the journal.
    \item Reviews fulfilling the smart-contract requirements are validated by the journal editors.
    \item When the reviews are accepted (\emph{bounty fulfillment}), reviewers awarded a token called \emph{ANT}.
    \item Not all reviews will have the same quality and depth. However, each of them might bring up one or more relevant contribution for the sake of improving the manuscript. In order to redistribute the bounty in a fair manner across reviewers, reviews will be voted by Anters (members of the community) via Quadratic Voting to rank the most prolific peer-reviewers.

@@

@@

AntsReview [\ref{appendix:b}] is the core of the smart contracts deployed on Ethereum Rinkeby's Testnet as shown in the flow-chart [Fig. \ref{fig:contracts}].
\newline It implements a Bounty-like system where an issuer (author) is asked a series of actions, to ensure transparency and robustness, regarding the AntReview that he's creating:
\begin{itemize}
  \item to upload the file containing the requirements of the peer-review and the paper into IPFS.
  \item to specify a deadline in the form of a unix timestamp after which the fulfillment will no longer be accepted.
  \item to send the amount of ether for the reward.
\end{itemize}

AntsReviewRoles[\ref{appendix:a}], to ensure integrity of the system, implements an access management, leveraging on AccessControl.sol by OpenZeppelin Library, through the creation of the Roles Issuer and Peer-Reviewer.
\newline It also integrates a circuit breaker design pattern via Pausable.sol by OpenZeppelin to allow the Pauser Role, that by default is the Owner of the Smart Contracts, to pause (or unpause) the functions in case of emergency.
\newline In this way, only the Issuer (author) can create a new AntReview.
\newline Once created, an AntReview is available to be fulfilled by Peer-Reviewers, uploading the peer-review on IPFS before the deadline.
\newline The AntReview after being validated is then accepted by the Issuer and paid equally between Peer-Reviewers.
\newline Also, the Issuer can cancel the AntReview at any time and withdraw the amount of ether staked.
\newline One of the key aspects of the protocol is the concept of Proof of Existence, introduced by Stuart Haber \& W. Scott Stornetta with the paper "How to time-stamp a digital document" \bibliography{}
\newline As the pioneers of blockchain an cited by Bitcoin whitepaper, they were in a mission to solve the problem of immutability of digital records that became reality with the Blockchain and Bitcoin as its first application.
\newline In Ethereum the concept of immutability is achieved via the blockchain and proof of work consesus algorithm by a chain of timestamped block hashes that are secured by miners competing computations.
\newline AntsReview is evaluating the advantages of storing the hashes of the peer-reviews into a Merkle Tree to achieve immutability and efficiency in verifying the data with a complexity of O(logn) for searching through the tree.
\newline A Merkle tree is a particular type of binary tree, formed by a set of nodes with a large set of leaf nodes at the bottom of the tree containing representing the hash of the original data, a set of intermediate nodes where each node is the sum of the two children hashes, ending with a single root hash.
\newline In order to verify if a specific hash is included into a Markle Tree, leveraging on MerkleProof.sol by OpenZeppelin Library, we need to provide a proof, generated from the leaf of interest, that represent the remification derived from the leaf, the root hash and finally the leaf we want to verify.
\newline The paper and peer-review documents will be included into a Merkle Tree by hashing the data using keccak256, a cryptographic hashing algorithm available in Solidiy, an object-oriented programming language for writing smart contracts that run on the Ethereum Virtual Machine (EVM).

@@

\begin{itemize}
  \item PseudoAnonimity granted by an Ethereum's Externally Owned Accounts (EOA) address that can pseudo-obscure the identity of the agent.
  \item Private Transactions allowed by AZTEC Protocol security layer via zkAnt. Future developments will allow to leverage on PLONK Proofs to reduce gas costs and improve scalability.
\end{itemize}

 Externally Owned Accounts (EOA) in Ethereum are controlled by private keys, are 20 bytes long and have no code. An user can send messages from an externally owned account by creating and signing a transaction.
\newline The limitation of such solution regarding the Privacy of the Protocol is due to the fact that blockchain and transactions are public so anyone can see the details of a transaction, browsing a block explorer like Etherscan, and also they're subjected to data mining to extract value and identify users in the blockchain.
\newline To avoid that, AntsReview will implement zkAnt, an Ant token wrapped into AZTEC Protocol, where leveraging on zkSNARKS, and PLONK in the future, will allow private transactions in the system to maintain the privacy and anonimiy of Peer-Reviewers.
\newline The AZTEC Protocol was conceived to enable privacy on public blockchains. It uses ZK-SNARKS to validate encrypted transactions.
\newline ZK-SNARKs (Zero-Knowledge Succinct Non-Interactive Argument of Knowledge) refers to a proof construction where one can prove possession of certain information, like a secret key, without revealing that information, and without any interaction between prover and verifier.
\newline Zero-Knowledge proofs allow an actor (prover) to prove to another (verifier) that a statement is true, without revealing any information apart from the validity of the statement itself.
\newline Future developments will investigate viable solutions, for scaling the system, like ZK-Rollups by AZTEC Protocol, one of the options being developed for a type of layer 2 construction that runs on top of Ethereum to improve scalability. This will enable to run smart contracts at scale with quasi-instant transactions while still being secured by Ethereum.
\subsubsection{Privacy/anonymity}. To enhance the peer-reviewer's privacy, we would like to implement zkANT, an ERC20 token, Ant, wrapped into AZTEC Protocol ZK-SNARKs, a non-interactive type of zero-knowledge privacy protocol to enable private transactions on Ethereum. Zero-knowledge proof is a mathematical cryptographic method that through values permutations allows one party (the prover) to prove to another (the verifier) the veracity of a statement, without having to reveal what the statement is. We will use ZK-SNARKs (which stands for “Zero-Knowledge Succinct Non-Interactive Argument of Knowledge”) via the open source libraries of AZTEC protocol. AZTEC, now TURBOPLONK bla bla (faster?) combines the confidentiality of the transactions (the value of the transaction is hidden, the amount of token (?) is not revealed thus preventing biases in the peer-review quadratic voting process = "I want to bet on this review because I want to win the bounty") with general-purpose computation (it's a Turing-complete Virtual Machine): this means transaction are not limited just to the local cryptocurrency (in our case ANT) but cross-asset trades are allowed (I can exchange ANT tokesn with other crypto-currencies).
\section{Discussions}
\subsection{A new community-driven standard?}
- a change is already happening: specially new born publishers are opening up review process (BioMed Central, ELife, Frontiers, PeerJ, F1000 Research) -- from 2020 also Nature declared that will do the same.
